Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that defines the common use cases identified. These
steps include the following: observations selection from the DataStore,  data
reduction, excess map computation, model fitting, flux-points estimation, and
light-curves production. The structure of the \code{Analysis} class allows to define
custom AnalysisStep, so ones could design and configure arbitrarily complex
wokflows. \todo{the latter is not true for v1.0..., include example YAML file?}

>>>>

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that defines the common use cases identified. These
steps include the following: observations selection with the \code{DataStore},  data
reduction, excess map computation, model fitting, flux-points estimation, and
light-curves production. The structure of the \code{Analysis} class allows to define
custom AnalysisStep, so ones could design and configure arbitrarily complex
wokflows. \todo{the latter is not true for v1.0..., include example YAML file?}
